---
title: "Modeling average_age_acquisition"
author: "Tilde Sloth"
date: "2023-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages      
```{r}
pacman::p_load(tidyverse, brms)
```

# Loading data
```{r}
AOA_data <- read_csv("../Data/wordbank_item_data.csv")
Centrality_t2_training <- read_csv("../Data/Centrality_t2_training.csv")
Centrality_t2_test <-  read_csv("../Data/Centrality_t2_test.csv")
Centrality_DF <- read_csv("../Data/Cleaned/CENTRALITY_DF.csv")
```
# Creating Centrality_DF_t2
```{r}
Centrality_DF_t2 <- Centrality_DF %>% 
    filter(Timepoint == 2)

# Remove duplicates based on all columns
Centrality_DF_t2 <- Centrality_DF_t2 %>% distinct()
```


# Cleaning up a bit
```{r}
#removing words that are sounds
AOA_data <- AOA_data %>%
  filter(category != "sounds")

#looking at the unique "more than one words"
more_than_one_word <- AOA_data[str_detect(AOA_data$item_definition, "\\s+"), ]

more_than_one_word_unique <- more_than_one_word %>% distinct(item_definition)

#removing words that are two words
AOA_data <- AOA_data %>%
  mutate(item_definition = gsub(" \\(.*", "", item_definition)) %>%
  filter(!grepl(" ", item_definition) | grepl(" \\(", item_definition))

#remove words that end with *
AOA_data <- AOA_data %>% 
  # Remove the * character from words that end with it
  mutate(item_definition = str_remove(item_definition, "\\*$"))

#change words with /
AOA_data <- AOA_data %>%
  # Remove everything after the /
  mutate(item_definition = str_remove_all(item_definition, "/.*"))
```

# Dealing with duplicates
```{r}
#unique words
length(unique(AOA_data$item_definition)) #618

list_of_words <- as.list(AOA_data$item_definition) #630

AOA_data %>% 
     group_by(item_definition) %>% 
     filter(n() > 1) %>% 
     ungroup %>% 
     arrange(item_definition)

# Removing the same words as in child_specific data
items_to_remove = c(220, 23, 412, 421, 424, 30, 129, 477, 486, 260, 154, 502)

for (i in items_to_remove){
    AOA_data <- subset(AOA_data, item_id != i)
}

```

# Removing unimportant columns
```{r}
#removing unimportant columns
AOA_data <- subset(AOA_data, select = -c(downloaded, item_id, category))
```

# Transform the dataset from wide to long format
```{r}
AOA_data <- AOA_data %>%
  pivot_longer(
    cols = c(-item_definition, ), # This will pivot all columns except for item_definition
    names_to = "Age_Months",
    values_to = "Percentage_Knowing"
  )
```

# Creating average age of acquisition column
```{r}
#calculate average age of acquisition
Average_age <- AOA_data %>% 
    group_by(item_definition) %>% 
    summarize(Average_Age_of_Acquisition = min(Age_Months[Percentage_Knowing > 0.5], na.rm = TRUE))

```


# Save it
```{r}
write.csv(AOA_data, file = "../Data/Cleaned_AOA.csv")
```

# Removing unimportant columns i Centrality_t2_training and Centrality_t2_test
```{r}
Centrality_t2_training <- subset(Centrality_t2_training, select = -c(Semantic_centrality, Phonological_centrality, Word_length_centrality, birth_order, caregiver_education, sex))

Centrality_t2_test <- subset(Centrality_t2_test, select = -c(Semantic_centrality, Phonological_centrality, Word_length_centrality, birth_order, caregiver_education, sex))

Centrality_DF_t2 <- subset(Centrality_DF_t2, select = -c(Semantic_centrality, Phonological_centrality, Word_length_centrality, birth_order, caregiver_education, sex))

```


# Merge AOA data with Centrality_DF
```{r}
merged_AOA_training <- merge(Average_age, Centrality_t2_training, by = "item_definition")

merged_AOA_test <- merge(Average_age, Centrality_t2_test, by = "item_definition")

merged_AOA <- merge(Average_age, Centrality_DF_t2, by = "item_definition")

#create binary variable that indicates whether the age of the child is equal to or above the average age of acquisition for that word
merged_AOA_training <- merged_AOA_training %>% 
    mutate(Expected_to_know_from_AOA = ifelse(age >= Average_Age_of_Acquisition, 1, 0))

merged_AOA_training <- merged_AOA_training %>% 
    mutate(Expected_to_know_from_AOA = as.factor(Expected_to_know_from_AOA))

merged_AOA_test <- merged_AOA_test %>% 
    mutate(Expected_to_know_from_AOA = ifelse(age >= Average_Age_of_Acquisition, 1, 0))

merged_AOA_test <- merged_AOA_test %>% 
    mutate(Expected_to_know_from_AOA = as.factor(Expected_to_know_from_AOA))

merged_AOA <- merged_AOA %>% 
    mutate(Expected_to_know_from_AOA = ifelse(age >= Average_Age_of_Acquisition, 1, 0))

merged_AOA <- merged_AOA %>% 
    mutate(Expected_to_know_from_AOA = as.factor(Expected_to_know_from_AOA))
```


```{r}
write.csv(merged_AOA_training, "../Data/mergedAOA_training.csv")
write.csv(merged_AOA_test, "../Data/mergedAOA_test.csv")
```



# Creating bayesian AOA model
```{r}
formula_AOA <- brms::bf(Knows_Word ~ Expected_to_know_from_AOA)

AOA_priors <- c(
    prior(normal(0, 10), class = b)
)

# AOA_model_for_accuracy <- brm(
#     formula = formula_AOA,
#     data = merged_AOA_training,
#     family = bernoulli,
#     backend = "cmdstanr",
#     prior = AOA_priors,
#     sample_prior = T,
#     iter = 1000,
#     warmup = 500,
#     cores = parallel::detectCores(),
#     chains = 2,
#     seed = 123,
#     threads = threading(2),
#     stan_model_args = list(stanc_options = list("O1")),
#     file = "../Models/AOA_training.rds"
# )

AOA_model_for_accuracy <-  readRDS("../Models/AOA_training.rds")
```
# Model for k-fold
```{r}
# AOA_model_for_kfold <- brm(
#     formula = formula_AOA,
#     data = merged_AOA,
#     family = bernoulli,
#     backend = "cmdstanr",
#     prior = AOA_priors,
#     sample_prior = T,
#     iter = 1000,
#     warmup = 500,
#     cores = parallel::detectCores(),
#     chains = 2,
#     seed = 123,
#     threads = threading(2),
#     stan_model_args = list(stanc_options = list("O1")),
#     file = "../Models/AOA_model_kfold.rds"
# )

AOA_model_for_kfold <-  readRDS("../Models/AOA_model_kfold.rds")
```


# here we will need some kind of K-fold or LOO
```{r}
# Performing K-fold
#k_fold_AOA <- kfold(AOA_model_for_kfold, K = 5)
#saveRDS(k_fold_AOA, "../Models/kfold_AOA.rds")
k_fold_AOA <-  readRDS("../Models/kfold_AOA.rds")
print(k_fold_AOA)
```


# Calculating simple accuracy - just for fun
```{r}
# Generate posterior predictions
posterior_predictions <- brms::posterior_predict(AOA_model_for_accuracy,
                newdata = merged_AOA_test)
    
# Calculate mean predicted probabilities for each observation
predicted_probs <- apply(posterior_predictions, 2, mean)

# Convert to binary predictions based on a threshold (e.g., 0.5)
predicted_classes <- ifelse(predicted_probs > 0.5, 1, 0)

# Assuming your test data has the actual outcomes in a column named 'Knows_Word'
actual_classes <- merged_AOA_test$Knows_Word

# Calculate accuracy
accuracy <- mean(predicted_classes == actual_classes)

# Print accuracy
print(paste("Accuracy:", accuracy))
```


