---
title: "Clean Network Measurement"
author: "Laurits Lymgbæk"
date: "2023-10-03"
output: html_document
---
# Setup for packages and functions
## Load packages
```{r}
### install.packages("pacman")
pacman::p_load(tidyverse, igraph, purrr)
```

## Load files
```{r}
# Load the data
Child_Data <- read_csv(file = "../Data/75kidsubset.csv") %>% 
    arrange(item_definition) %>% 
    arrange(child_id) %>% 
    arrange(age)#Subset of data for quick functions
# Data <- read_csv("Insert_not_subset here") #Total dataset

# Load semantics df
semantics_csv <- read_csv(file = "../Data/semantic_distances.csv")
## This matrix has row names as a column
ADJ_MATRIX_SEMANTICS <- as.matrix(semantics_csv[,-1]) # Save a copy without the name-column
rownames(ADJ_MATRIX_SEMANTICS) <- semantics_csv$...1 # Set the row names of the copied matrix as the name-column from the original matrix
WORD_LIST <- semantics_csv$...1 # Save a list of words that a child can learn 


# Load phonetic distance df
phonetics_csv <- read_csv(file = "../Data/phonetic_distance_normalized.csv")
## Make a matrix and save rownames
ADJ_MATRIX_PHONETICS <- as.matrix(phonetics_csv[,-1])
rownames(ADJ_MATRIX_PHONETICS) <- phonetics_csv$...1

# Clean up environment
rm(phonetics_csv, semantics_csv)
```

## Filter this data futher, so we only have data for one kid
```{r}
Child_ID <- 7 # The child we want to investigate
Time_ID <- 2 # The timepoint for this child

filtered_Words_for_child <- Child_Data %>% 
    filter(child_id == unique(child_id)[Child_ID]) %>% #Only pick this child
    arrange(age) %>%
    filter(age == unique(age)[Time_ID]) # For this age (smallest and up)
```


## Find mean of 3rd quantile for numbers in semantics matrix
```{r}
Summary_of_semantics <- as.data.frame(summary(ADJ_MATRIX_SEMANTICS))[,2:3] %>%
    separate_wider_delim(cols = Freq,delim = ":",names = c("Summary_Name", "Summary_Number")) %>% 
    mutate(Summary_Name = str_trim(Summary_Name),
           Summary_Number = as.numeric(str_trim(Summary_Number)))

q3_semantics <- Summary_of_semantics %>% 
     filter(Summary_Name == "3rd Qu.")




mean_of_q3 <- mean(q3_semantics$Summary_Number)

rm(Summary_of_semantics, q3_semantics) # Clean up environment

```

### Create a adj matrix of semantic edges
```{r}
# Create matrix edges
SEMANTIC_EDGES_MATRIX <- ifelse(ADJ_MATRIX_SEMANTICS>=mean_of_q3,yes = 1,no = 0)
# find relationship between: Edges / Verticies
sum(SEMANTIC_EDGES_MATRIX)/length(SEMANTIC_EDGES_MATRIX)

```
## Create adj matrix for child N where an edge occurs if the child know both words.
```{r}
filtered_Words_for_child %>% 
    select(item_definition,value) %>% 
    arrange((item_definition)) %>% 
    arrange(desc(value))

KNOWN_WORDS_NUMERIC <- filtered_Words_for_child$value
KNOWN_WORDS_STRING <-  filtered_Words_for_child$item_definition


# Create adjacency matrix
KNOWN_WORDS_IDENTIFICATION_MATRIX <- matrix(abs(outer(KNOWN_WORDS_NUMERIC, KNOWN_WORDS_NUMERIC, FUN = "*")), # Create values for matrix
                           nrow = length(KNOWN_WORDS_STRING), ncol = length(KNOWN_WORDS_STRING), # Define size of matrix
                           dimnames = list(KNOWN_WORDS_STRING, KNOWN_WORDS_STRING)) #Give names to dimensions


id_matrix <- diag(length(KNOWN_WORDS_IDENTIFICATION_MATRIX[1,])) # Create a identity matrix of length(adjaceny_matrix)
REMOVE_SELF_EDGES <- KNOWN_WORDS_IDENTIFICATION_MATRIX*id_matrix # Create a matrix that has a 1 if the word triggers an edge with itself.
KNOWN_WORDS_IDENTIFICATION_MATRIX <- KNOWN_WORDS_IDENTIFICATION_MATRIX - REMOVE_SELF_EDGES # Remove self edges from known words matrix

```



### Multiply known_words_martrix with semantics_edges_matrix and divide with / 2
```{r}
CHILD_N_SEMATNIC_EDGES_AT_TIME_N <- SEMANTIC_EDGES_MATRIX * KNOWN_WORDS_IDENTIFICATION_MATRIX

GRAPH_OBJECT <- graph_from_adjacency_matrix(CHILD_N_SEMATNIC_EDGES_AT_TIME_N, mode = "undirected")

V(GRAPH_OBJECT)$size <- 1
#V(GRAPH_OBJECT)$label <-
E(GRAPH_OBJECT)$arrow.mode <- 0
#plot(GRAPH_OBJECT)
```


```{r}
## Create a Unknown variable that contains all words not known by the child.
names_to_remove <- filtered_Words_for_child %>% 
    filter(filtered_Words_for_child$value == 0)
names_to_remove <- names_to_remove$item_definition
vertices_to_remove <- which(V(GRAPH_OBJECT)$name %in% names_to_remove)

GRAPH_OBJECT = delete.vertices(GRAPH_OBJECT, vertices_to_remove)

l <- layout_with_kk(GRAPH_OBJECT)
# l <- layout_with_fr(GRAPH_OBJECT)
# l <- layout_in_circle(GRAPH_OBJECT)

plot(GRAPH_OBJECT, layout=l)
vertices(GRAPH_OBJECT)
centralization.closeness(GRAPH_OBJECT)

```


## Try and save the graph for all words in a vector
```{r}
nested_graph <- list(GRAPH_OBJECT) # Wrap list to allow for rep
list_of_graphs <- rep(nested_graph,618) # Repeat list 618 times
names(list_of_graphs) <-  KNOWN_WORDS_STRING # Name the graphs
```



# Generalizing adding an edge (making a functionish)
```{r}
## TRY TO GENERALISE THE EDGES ##
### Save grandma in var
word_to_find_edges_for <-  "grandma"
### Check if the word exists in the list of 618 words
word_to_find_edges_for %in% KNOWN_WORDS_STRING

### Only pick the semantic edges for grandma:
edges_for_word <- SEMANTIC_EDGES_MATRIX[,word_to_find_edges_for]

### Save verticies (words) from graph:
verticies_in_graph <- V(GRAPH_OBJECT)$name


edges_to_graph_vertices <- edges_for_word[names(edges_for_word) %in% verticies_in_graph]

edges_to_graph_vertices_true <- names(edges_to_graph_vertices[which(edges_to_graph_vertices==1)])

edge_list <- c(#Make df into a string again
    rbind( # Bind word_to_find_edges_for before each edge
        word_to_find_edges_for,edges_to_graph_vertices_true))

```



# Try to add alligator word to graph
```{r}
GRAPH_OBJECT[] # See adj matrix before starting

# add add vertice and edges to list
GRAPH_OBJECT_2 <- GRAPH_OBJECT + 
    word_to_find_edges_for + #insert vertice without edges
    edges(edge_list) #add edges from vertice to other vertices
    
GRAPH_OBJECT_2[]

centralization.betweenness(graph = GRAPH_OBJECT_2,directed = FALSE)
```













