---
title: "Clean_Adj_Matrix"
author: "Laurits Lyngbæk"
date: "2023-10-10"
output: html_document
---

# SETUP
## LOAD PACKAGES
```{r}
### install.packages("pacman")
pacman::p_load(tidyverse)
```

# Create semantics matrix
## Load Semantics
```{r}
# Load semantics df
semantics_csv <- read_csv(file = "../Data/semantic_distances.csv")
## This matrix has row names as a column
ADJ_MATRIX_SEMANTICS <- as.matrix(semantics_csv[,-1]) # Save a copy without the name-column
rownames(ADJ_MATRIX_SEMANTICS) <- semantics_csv$...1 # Set the row names of the copied matrix as the name-column from the original matrix
```

## Find mean of 3rd quantile for numbers in semantics matrix
```{r}

# Create a summary of adj matrix and split strings so we can filter for statistic and get the number
Summary_of_semantics <- as.data.frame(summary(ADJ_MATRIX_SEMANTICS))[,2:3] %>%
    separate_wider_delim(cols = Freq,delim = ":",names = c("Summary_Name", "Summary_Number")) %>% 
    mutate(Summary_Name = str_trim(Summary_Name),
           Summary_Number = as.numeric(str_trim(Summary_Number)))

# Filter for the 3rd quantile of each row
q3_semantics <- Summary_of_semantics %>% 
     filter(Summary_Name == "3rd Qu.")

# Find the mean 3rd quantile value
mean_of_q3 <- mean(q3_semantics$Summary_Number)
hist(x = q3_semantics$Summary_Number, main = title(paste("The mean 3rd quantile value is", round(mean_of_q3,2)))
     )

rm(Summary_of_semantics, q3_semantics, Summary_of_semantics) # Clean up environment
```

### Create a adj matrix of semantic edges
```{r}
# Create matrix edges
SEMANTIC_EDGES_MATRIX <- ifelse(ADJ_MATRIX_SEMANTICS>=mean_of_q3,yes = 1,no = 0)


rm(q3_semantics, mean_of_q3, ADJ_MATRIX_SEMANTICS)
```
### Make sure no vertices has an edge to themselves
```{r}
ID_matrix <- diag( #Create a identity matrix
    length(SEMANTIC_EDGES_MATRIX[1,])) #of length of matrix (618)
NO_SELF_EDGES <- (ID_matrix-1)*-1

SEMANTIC_EDGES_MATRIX <- SEMANTIC_EDGES_MATRIX*NO_SELF_EDGES

```


## Save matrix
```{r}
write.table(SEMANTIC_EDGES_MATRIX, '../Data/Cleaned/SEMANTIC_EDGES_MATRIX.txt', sep = ",")
```



# Create phonological matrix
## Load Semantics
```{r}
# Load semantics df
phonetic_distance <- read_csv(file = "../Data/phonetic_distance.csv")
## This matrix has row names as a column
ADJ_PHONETIC_DISTANCE <- as.matrix(phonetic_distance[,-1]) # Save a copy without the name-column
rownames(ADJ_PHONETIC_DISTANCE) <- phonetic_distance$...1 # Set the row names of the copied matrix as the name-column from the original matrix
```

## Find mean of 3rd quantile for numbers in semantics matrix
```{r}

# Create a summary of adj matrix and split strings so we can filter for statistic and get the number
Summary_of_phonetics <- as.data.frame(summary(ADJ_PHONETIC_DISTANCE))[,2:3] %>%
    separate_wider_delim(cols = Freq,delim = ":",names = c("Summary_Name", "Summary_Number")) %>% 
    mutate(Summary_Name = str_trim(Summary_Name),
           Summary_Number = as.numeric(str_trim(Summary_Number)))

# Filter for the 3rd quantile of each row
q1_phonetics <- Summary_of_phonetics %>% 
     filter(Summary_Name == "1st Qu.")

# Find the mean 3rd quantile value
mean_of_q1 <- mean(q1_phonetics$Summary_Number)
hist(x = q1_phonetics$Summary_Number, main = title(paste("The mean 1st quantile value is", round(mean_of_q1,2))))

rm(Summary_of_semantics, q3_semantics, Summary_of_semantics) # Clean up environment
```

### Create a adj matrix of semantic edges
```{r}
# Create matrix edges
PHONETIC_EDGES_MATRIX <- ifelse(ADJ_PHONETIC_DISTANCE<=2,yes = 1,no = 0)


rm(q1_semantics, mean_of_q1, ADJ_MATRIX_SEMANTICS)
```
### Make sure no vertices has an edge to themselves
```{r}
ID_matrix <- diag( #Create a identity matrix
    length(PHONETIC_EDGES_MATRIX[1,])) #of length of matrix (618)
NO_SELF_EDGES <- (ID_matrix-1)*-1

PHONETIC_EDGES_MATRIX <- PHONETIC_EDGES_MATRIX*NO_SELF_EDGES

```


## Save matrix
```{r}
write.table(PHONETIC_EDGES_MATRIX, '../Data/Cleaned/PHONETIC_EDGES_MATRIX.txt', sep = ",")
```



