---
title: "Creating_Networks_From_Functions"
author: "Laurits Lyngbæk"
date: "2023-10-10"
output: html_document
---
# SETUP
## Load packages
```{r}
### install.packages("pacman")
pacman::p_load(tidyverse, igraph, purrr)
```

## Load files into into the environment
All files need to be either the child data or a cleaned adjacency matrix:
```{r}
<<<<<<< HEAD
# # Load the child data 
# Child_Dataframe <- read_csv(file = "../Data/Cleaned_USA.csv") %>% #Subset of data for quick functions
#     arrange(item_definition) %>% # sorter dataen
#     arrange(child_id) %>% 
#     arrange(age) %>% 
#     distinct(child_id, age,item_definition, .keep_all = TRUE) #Make sure all children are 618 length matrix, by removing duplicates

# Alternative SUBSET VERSION
Child_Dataframe_subset <- read_csv(file = "../Data/75kidsubset.csv") %>% #Subset of data for quick functions
    arrange(item_definition) %>% # sorter dataen
    arrange(child_id) %>%
    arrange(age) %>% 
    distinct(child_id, age,item_definition, .keep_all = TRUE) #Make sure all children are 618 length matrix, by removing duplicates
=======
# Load the child data 
Child_Dataframe <- read_csv(file = "../Data/75kidsubset.csv") %>% #Subset of data for quick functions
    arrange(item_definition) %>% # sorter dataen
    arrange(child_id) %>% 
    arrange(age) 
# %>% 
    # mutate(item_definition = ifelse(item_definition == "break", "breaks", item_definition))%>% 
    # mutate(item_definition = ifelse(item_definition == "don't", "dont", item_definition))

>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
# Load semantics df
SEMANTIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/SEMANTIC_EDGES_MATRIX.txt", sep = ","))

# Load phonetic distance df
PHONETIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/PHONETIC_EDGES_MATRIX.txt", sep = ","))

```

# Define Functions
## Create a functions that subsets a child_id at time one or two
```{r}
FUNC_Subset <- function(dataframe, column_name, true_value){
    #' This functions returns a subset of the data frame, where the column_name == name_id
    filtered_df <- subset(dataframe, dataframe[, column_name] == true_value)
    return(filtered_df)
}

FUNC_Subset_first_unique <- function(dataframe, column_name){
    #' Arrange a dataframe
    dataframe <- arrange(dataframe, {{column_name}})
    unique_timepoints <- unique(dataframe[[column_name]])
    filtered_df <- subset(dataframe, dataframe[, column_name] == unique_timepoints[1])
    return(filtered_df)
}

FUNC_Subset_second_unique <- function(dataframe, column_name){
    #' Arrange a dataframe
    dataframe <- arrange(dataframe, {{column_name}})
    unique_timepoints <- unique(dataframe[[column_name]])
    filtered_df <- subset(dataframe, dataframe[, column_name] == unique_timepoints[2])
    return(filtered_df)
}


FUNC_Subset_child_at_first_unique_age <- function(dataframe, ID_collumn_name, ID_String, Age_collumn_name){
    # Make a unique local subset for this child
    subset <- FUNC_Subset(dataframe = dataframe,
            column_name = ID_collumn_name, 
            true_value = ID_String)
    # Subset the first unique age
    subset <- FUNC_Subset_first_unique(
        dataframe = subset,
        column_name = Age_collumn_name)
    return(subset)
}

FUNC_Subset_child_at_second_unique_age <- function(dataframe, ID_collumn_name, ID_String, Age_collumn_name){
    # Make a unique local subset for this child
    subset <- FUNC_Subset(dataframe = dataframe,
            column_name = ID_collumn_name,
            true_value = ID_String)
    # Subset the first unique age
    subset <- FUNC_Subset_second_unique(
        dataframe = subset,
        column_name = Age_collumn_name)
    return(subset)
}


# # END RESULTS
# FUNC_Subset_child_at_first_unique_age(Child_Dataframe, ID_collumn_name, Child_ID, Age_collumn_name)
# FUNC_Subset_child_at_second_unique_age(Child_Dataframe, ID_collumn_name, Child_ID, Age_collumn_name)
```

## Create a function that returns a list of unique names
```{r}
FUNC_Get_List_Of_Unique_Child_ID <- function(dataframe, ID_collumn_name){
    Unique_IDs <- unique(dataframe[[ID_collumn_name]])
    return(Unique_IDs)}
```


## Create a function that defines a adjacency matrix of words known for a unique child at unique timepoint
```{r}

FUNC_Get_known_words_matrix <- function(Subset_dataframe, Is_word_know_collumn_name, Word_string_collumn_name){
    #' This function returns a adjacency matrix, where 1 indicates the child knows both words.
    # Define child as two string
    KNOWN_WORDS_NUMERIC <- Subset_dataframe[[Is_word_know_collumn_name]]
    KNOWN_WORDS_STRING <- Subset_dataframe[[Word_string_collumn_name]]
 
    # Create adjacency matrix
    KNOWN_WORDS_IDENTIFICATION_MATRIX <- matrix(abs(outer(KNOWN_WORDS_NUMERIC, KNOWN_WORDS_NUMERIC, FUN = "*")), # Create values for matrix
                           nrow = length(KNOWN_WORDS_STRING), ncol = length(KNOWN_WORDS_STRING), # Define size of matrix
                           dimnames = list(KNOWN_WORDS_STRING, KNOWN_WORDS_STRING)) #Give names to dimensions

    # Remove edges between words that are connected to themselves 
    ID_MATRIX <- diag(length(KNOWN_WORDS_IDENTIFICATION_MATRIX[1,])) # Create a identity matrix of length(adjaceny_matrix)
    REMOVE_SELF_EDGES <- KNOWN_WORDS_IDENTIFICATION_MATRIX*ID_MATRIX # Create a matrix that has a 1 if the word triggers an edge with itself.
    KNOWN_WORDS_IDENTIFICATION_MATRIX <- KNOWN_WORDS_IDENTIFICATION_MATRIX - REMOVE_SELF_EDGES # Remove self edges from known words matrix
    
    return(KNOWN_WORDS_IDENTIFICATION_MATRIX)   
}
```




## Use Known_words_matrix to create a personalized ADJ_MATRIX for a linguistic adj matrix 
```{r}
FUNC_Personalised_ling_adj_matrix <- function(Personalized_Matrix, Linguistic_Matrix){
    #' This function takes two equally sized matrix' and multiplies them, this results in only edges between words known to the child being saved.
    Personalized_Linguistic_Matrix <- Personalized_Matrix * Linguistic_Matrix
    return(Personalized_Linguistic_Matrix)}


FUNC_Create_a_Graph_And_Remove_unknown_words <- function(Subset_dataframe,
                                                         Personalized_Adj_Linguistic_Matrix,
                                                         Is_word_know_collumn_name, 
                                                         Word_string_collumn_name){
    #' Requires IGRAPH package
    GRAPH_OBJECT <- graph_from_adjacency_matrix(Personalized_Adj_Linguistic_Matrix, mode = "undirected")
    NAMES_TO_REMOVE <- FUNC_Subset(dataframe = Subset_dataframe,
                column_name = Is_word_know_collumn_name,
                true_value = 0)
    NAMES_TO_REMOVE <- NAMES_TO_REMOVE[[Word_string_collumn_name]]
    VERTICES_TO_REMOVE <- which(V(GRAPH_OBJECT)$name %in% NAMES_TO_REMOVE)
    GRAPH_OBJECT <-  delete.vertices(GRAPH_OBJECT, VERTICES_TO_REMOVE)
    return(GRAPH_OBJECT)
}
```

## Create a function that duplicate your graph in a named list for each 
```{r}
FUNC_Tranform_graph_to_list_of_graphs <-  function(GRAPH_OBJECT, KNOWN_WORDS_STRING){
    NESTED_GRAPH <- list(GRAPH_OBJECT) # Wrap list to allow for rep
    LIST_OF_GRAPHS <- rep(NESTED_GRAPH,length(KNOWN_WORDS_STRING)) # Repeat list 618 times
    names(LIST_OF_GRAPHS) <-  KNOWN_WORDS_STRING # Name the graphs
    return(LIST_OF_GRAPHS)
}
```

## Create a function that adds a new word and its edges to the graph
```{r}

FUNC_Add_new_word_to_graph <- function(GRAPH_OBJECT, NEW_WORD_STRING, ADJ_MATRIX){
    if (NEW_WORD_STRING %in% V(GRAPH_OBJECT)$name){
        return(GRAPH_OBJECT)
    }
    
    VECTOR_OF_NAMES <- colnames(ADJ_MATRIX) # GET A VECTOR OF STRING TO BE ABLE TO which(vector == "value"), as matrix[,"x"] breaks with certain strings
    ### Only pick the semantic edges for NEW_WORD_STRING
    EDGES <- ADJ_MATRIX[,which(VECTOR_OF_NAMES == NEW_WORD_STRING)]
    
    ### Save verticies (words) from graph:
    VERTICES_IN_GRAPH <- V(GRAPH_OBJECT)$name
    
    
    NAMED_EDGES_OF_VERTICIES <- EDGES[names(EDGES) %in% VERTICES_IN_GRAPH]
    EDGES_OF_VERTICIES <- names(NAMED_EDGES_OF_VERTICIES[which(NAMED_EDGES_OF_VERTICIES==1)])
    
    #Make df into a string again
    EDGE_LIST <- c(
        rbind( # Bind NEW_WORD_STRING before each edge
            NEW_WORD_STRING,EDGES_OF_VERTICIES))
    
    
    if (length(EDGE_LIST) > 1){
        GRAPH_OBJECT <- GRAPH_OBJECT + 
            NEW_WORD_STRING + #insert vertice without edges
            edges(EDGE_LIST) #add edges from vertice to other vertices
    } else {
        GRAPH_OBJECT <- GRAPH_OBJECT + NEW_WORD_STRING
    }
    
    return(GRAPH_OBJECT)
<<<<<<< HEAD
}


## NESTED VERSION
# Return_list_of_updated <- imap(List_of_List_of_Graphs[[1]], FUNC_nested_add_word_to_graph_for_imap, MATRIX = SEMANTIC_EDGES_MATRIX)
FUNC_nested_add_word_to_graph_for_imap <- function(igraph_object, index, MATRIX) {
    global_counter <<- global_counter + 1
    cat("Global Counter:", global_counter)
    #' Add the new word to the igraph
    igraph_object <- FUNC_Add_new_word_to_graph(
        GRAPH_OBJECT = igraph_object,
        NEW_WORD_STRING = index,
        ADJ_MATRIX = MATRIX)
    return(igraph_object)  # You can return the modified graph or any other result
}

=======
    }
>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
```

# Run Functions
## Set variables
```{r}
<<<<<<< HEAD
EDGE_MATRIX_ID <- SEMANTIC_EDGES_MATRIX # The adjacency edge matrix that is inputed in functions
Child_Dataframe <-  Child_Dataframe_subset # The dataset that contains all information regarding the children
=======
Edge_Matrix_ID <- SEMANTIC_EDGES_MATRIX # The adjacency edge matrix that is inputed in functions
Child_Dataframe <-  Child_Dataframe # The dataset that contains all information regarding the children
>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
ID_collumn_name <- "child_id"
Age_collumn_name <- "age"
Unique_Children <- FUNC_Get_List_Of_Unique_Child_ID(Child_Dataframe, ID_collumn_name)
Child_ID <- Unique_Children[6]
Is_word_known_collumn_name = "value"
Word_string_collumn_name = "item_definition"
Word_numeric_column_name = "item_id"

KNOWN_WORDS_NUMERIC <- unique(Child_Dataframe[[Word_numeric_column_name]]) 
KNOWN_WORDS_STRING <-  unique(Child_Dataframe[[Word_string_collumn_name]]) 
KNOWN_WORDS_STRING[75] <- "breaks"
```

## Execution Block
```{r}
# Run for one child, find subset
child_1414_1<- FUNC_Subset_child_at_first_unique_age(
    dataframe = Child_Dataframe,
    ID_collumn_name = ID_collumn_name,
    ID_String =  Child_ID,
    Age_collumn_name =  Age_collumn_name)

# Make adj matrix
Personalized_Adj_Matrix <- FUNC_Get_known_words_matrix(
    Subset_dataframe = child_1414_1,
    Is_word_know_collumn_name =  Is_word_known_collumn_name,
    Word_string_collumn_name = Word_string_collumn_name)

<<<<<<< HEAD

# Make a list of subsets (3.91 seconds as subset -> 38.8 seconds at full dataset)
start_time <- Sys.time()
List_of_subsets <- purrr::map(.x =  List_of_subsets, 
                       .f = FUNC_Subset_child_at_first_unique_age,
                       dataframe = Child_Dataframe,
                       ID_collumn_name = ID_collumn_name,
                       Age_collumn_name = Age_collumn_name,
                       ID_String = ) #Nothing defined here to show that the map .x map value is used
end_time <- Sys.time()
end_time - start_time

start_time <- Sys.time()
# Make adj matrix' (0.80 seconds at subset -> 8.02 seconds at full dataset)
List_of_personalized_adj_matrix <- purrr::map(.x = List_of_subsets,
                                       .f = FUNC_Get_known_words_matrix,
                                       Subset_dataframe = , #left empty to show .x map value
                                       Is_word_know_collumn_name =  Is_word_known_collumn_name,
                                       Word_string_collumn_name = Word_string_collumn_name)
end_time <- Sys.time()
end_time - start_time

# Convert the personalized matrix to a lingisicually corrected matrix (0.223 seconds)
List_of_personalized_adj_matrix <- purrr::map(
    .x = List_of_personalized_adj_matrix, 
    .f = FUNC_Personalised_ling_adj_matrix,
    Personalized_Matrix = ,#left empty to show .x map value
    Linguistic_Matrix = EDGE_MATRIX_ID)

    
=======
# Get semantic adj matrix
Personalized_Adj_Linguistic_Matrix <- 
    FUNC_Personalised_ling_adj_matrix(
    Personalized_Matrix = Personalized_Adj_Matrix,
    Linguistic_Matrix = SEMANTIC_EDGES_MATRIX)
>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
```


## Create a GRAPH
```{r}
<<<<<<< HEAD
# Using a parralel map to make a graph and remove words from the two matrix (2.35 seconds -> 18.65)
start_time <- Sys.time()
List_of_graphs <- purrr::map2(.x = List_of_subsets, 
                       .y = List_of_personalized_adj_matrix,
                       .f = FUNC_Create_a_Graph_And_Remove_unknown_words,
                       Is_word_know_collumn_name = Is_word_known_collumn_name,
                       Word_string_collumn_name =  Word_string_collumn_name,
                       Subset_dataframe = , #This is where .x parameter goes
                       Personalized_Adj_Linguistic_Matrix = )#This is where .y parameter goes
end_time <- Sys.time()
end_time - start_time
=======
GRAPH <- FUNC_Create_a_Graph_And_Remove_unknown_words(
    Subset_dataframe = child_1414_1,
    Personalized_Adj_Linguistic_Matrix = Personalized_Adj_Linguistic_Matrix, 
    Is_word_know_collumn_name = Is_word_known_collumn_name,
    Word_string_collumn_name =  Word_string_collumn_name)
>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
```

## Make a list graphs
```{r}
<<<<<<< HEAD
# (0.03 seconds)
List_of_List_of_graphs <- purrr::map(.x = List_of_graphs,
            .f = FUNC_Tranform_graph_to_list_of_graphs,
    GRAPH_OBJECT = ,#This is where .x parameter goes
=======
List_of_Graphs <- FUNC_Tranform_graph_to_list_of_graphs(
    GRAPH_OBJECT = GRAPH,
>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
    KNOWN_WORDS_STRING = KNOWN_WORDS_STRING)

List_of_List_of_Graphs <- FUNC_Tranform_graph_to_list_of_graphs(
    GRAPH_OBJECT = List_of_Graphs,
    KNOWN_WORDS_STRING = c("test1","test2","test3"))

```


```{r}
<<<<<<< HEAD
global_counter <- 0
start_time <- Sys.time()
# Make a nested function with a map function inside: (63.5 seconds (2.6 mins if prins counter) ->  1.07352 hours (388104 runs of function))
List_of_List_of_graphs <- purrr::map(List_of_List_of_graphs, function(inner_list) {
    imap(inner_list, FUNC_nested_add_word_to_graph_for_imap, MATRIX = EDGE_MATRIX_ID)
})

end_time <- Sys.time()
end_time - start_time
# #Save this list
# saveRDS(List_of_List_of_graphs, file = "../Data/Subset_list_of_semantic_graphs")
# List_of_List_of_graphs <- readRDS("../Data/Subset_list_of_semantic_graphs")
```

# Get centrality from graphs
```{r}
start_time <- Sys.time()
# 20.3 seconds -> 23 mins
List_of_centrality <-  purrr::map(List_of_List_of_graphs, function(inner_list) {
    imap(inner_list, function(graph_object, index){
        eigen_centrality(graph_object, directed = FALSE)$vector[index]
    })
})
end_time <- Sys.time()
end_time - start_time
```
# Transform into dataframe:
```{r}
start_time <- Sys.time()
#(0.05 seconds)
DF_Centrality <- rrapply::rrapply(List_of_centrality, how = "melt") %>% 
    rename(Child_ID = L1,
           item_definition = L2) %>% 
    mutate(timepoint = timepoint,
           value = format(value, scientific = FALSE))
end_time <- Sys.time()
end_time - start_time
=======
names(List_of_Graphs)[613]
List_of_Graphs[[613]]

List_of_Graphs[[613]]<- FUNC_Add_new_word_to_graph(
    GRAPH_OBJECT = List_of_Graphs[[613]],
    NEW_WORD_STRING = names(List_of_Graphs)[613],
    ADJ_MATRIX = SEMANTIC_EDGES_MATRIX)

List_of_List_of_Graphs[[1]][3]
names(List_of_List_of_Graphs[[1]])[1]




>>>>>>> parent of c82a452 (Able to get centrality out for all children in subset, trying to generalize to all data)
```







