---
title: "Creating_Networks_From_Functions"
author: "Laurits Lyngbæk"
date: "2023-10-10"
output: html_document
---
# SETUP
## Load packages
```{r}
### install.packages("pacman")
pacman::p_load(tidyverse, igraph, purrr)
```

## Load files into into the environment
All files need to be either the child data or a cleaned adjacency matrix:
```{r}
# Load the child data 
Child_Dataframe <- read_csv(file = "../Data/75kidsubset.csv") %>% #Subset of data for quick functions
    arrange(item_definition) %>% # sorter dataen
    arrange(child_id) %>% 
    arrange(age)

# Load semantics df
SEMANTIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/SEMANTIC_EDGES_MATRIX.txt", sep = ","))

# Load phonetic distance df
PHONETIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/PHONETIC_EDGES_MATRIX.txt", sep = ","))

```



# Define Functions

## Create a functions that subsets a child_id at time one or two
```{r}
FUNC_Subset <- function(dataframe, column_name, true_value){
    #' This functions returns a subset of the data frame, where the column_name == name_id
    filtered_df <- subset(dataframe, dataframe[, column_name] == true_value)
    return(filtered_df)
}

FUNC_Subset_first_unique <- function(dataframe, column_name){
    #' Arrange a dataframe
    dataframe <- arrange(dataframe, {{column_name}})
    unique_timepoints <- unique(dataframe[[column_name]])
    filtered_df <- subset(dataframe, dataframe[, column_name] == unique_timepoints[1])
    return(filtered_df)
}

FUNC_Subset_second_unique <- function(dataframe, column_name){
    #' Arrange a dataframe
    dataframe <- arrange(dataframe, {{column_name}})
    unique_timepoints <- unique(dataframe[[column_name]])
    filtered_df <- subset(dataframe, dataframe[, column_name] == unique_timepoints[2])
    return(filtered_df)
}


FUNC_Subset_child_at_first_unique_age <- function(dataframe, ID_collumn_name, ID_String, Age_collumn_name){
    # Make a unique local subset for this child
    subset <- FUNC_Subset(dataframe = dataframe,
            column_name = ID_collumn_name, 
            true_value = ID_String)
    # Subset the first unique age
    subset <- FUNC_Subset_first_unique(
        dataframe = subset,
        column_name = Age_collumn_name)
    return(subset)
}

FUNC_Subset_child_at_second_unique_age <- function(dataframe, ID_collumn_name, ID_String, Age_collumn_name){
    # Make a unique local subset for this child
    subset <- FUNC_Subset(dataframe = dataframe,
            column_name = ID_collumn_name,
            true_value = ID_String)
    # Subset the first unique age
    subset <- FUNC_Subset_second_unique(
        dataframe = subset,
        column_name = Age_collumn_name)
    return(subset)
}


# # END RESULTS
# FUNC_Subset_child_at_first_unique_age(Child_Dataframe, ID_collumn_name, Child_ID, Age_collumn_name)
# FUNC_Subset_child_at_second_unique_age(Child_Dataframe, ID_collumn_name, Child_ID, Age_collumn_name)
```

## Create a function that returns a list of unique names
```{r}
FUNC_Get_List_Of_Unique_Child_ID <- function(dataframe, ID_collumn_name){
    Unique_IDs <- unique(dataframe[[ID_collumn_name]])
    return(Unique_IDs)}
```




## Create a function that defines a adjacency matrix of words known for a unique child at unique timepoint
```{r}

FUNC_Get_known_words_matrix <- function(Subset_dataframe, Is_word_know_collumn_name, Word_string_collumn_name){
    #' This function returns a adjacency matrix, where 1 indicates the child knows both words.
    # Define child as two string
    KNOWN_WORDS_NUMERIC <- Subset_dataframe[[Is_word_know_collumn_name]] 
    KNOWN_WORDS_STRING <-  Subset_dataframe[[Word_string_collumn_name]]
 
    # Create adjacency matrix
    KNOWN_WORDS_IDENTIFICATION_MATRIX <- matrix(abs(outer(KNOWN_WORDS_NUMERIC, KNOWN_WORDS_NUMERIC, FUN = "*")), # Create values for matrix
                           nrow = length(KNOWN_WORDS_STRING), ncol = length(KNOWN_WORDS_STRING), # Define size of matrix
                           dimnames = list(KNOWN_WORDS_STRING, KNOWN_WORDS_STRING)) #Give names to dimensions

    # Remove edges between words that are connected to themselves 
    ID_MATRIX <- diag(length(KNOWN_WORDS_IDENTIFICATION_MATRIX[1,])) # Create a identity matrix of length(adjaceny_matrix)
    REMOVE_SELF_EDGES <- KNOWN_WORDS_IDENTIFICATION_MATRIX*ID_MATRIX # Create a matrix that has a 1 if the word triggers an edge with itself.
    KNOWN_WORDS_IDENTIFICATION_MATRIX <- KNOWN_WORDS_IDENTIFICATION_MATRIX - REMOVE_SELF_EDGES # Remove self edges from known words matrix
    
    return(KNOWN_WORDS_IDENTIFICATION_MATRIX)   
}
```




# Use Known_words_matrix to create a personalized ADJ_MATRIX for a linguistic adj matrix 
```{r}
FUNC_Personalised_ling_adj_matrix <- function(Personalized_Matrix, Linguistic_Matrix){
    #' This function takes two equally sized matrix' and multiplies them, this results in only edges between words known to the child being saved.
    Personalized_Linguistic_Matrix <- Personalized_Matrix * Linguistic_Matrix
    return(Personalized_Linguistic_Matrix)}


FUNC_Create_a_Graph_And_Remove_unknown_words <- function(Subset_dataframe,
                                                         Personalized_Adj_Linguistic_Matrix,
                                                         Is_word_know_collumn_name, 
                                                         Word_string_collumn_name){
    #' Requires IGRAPH package
    GRAPH_OBJECT <- graph_from_adjacency_matrix(Personalized_Adj_Linguistic_Matrix, mode = "undirected")
    NAMES_TO_REMOVE <- FUNC_Subset(dataframe = Subset_dataframe,
                column_name = Is_word_know_collumn_name,
                true_value = 0)
    NAMES_TO_REMOVE <- NAMES_TO_REMOVE[[Word_string_collumn_name]]
    VERTICES_TO_REMOVE <- which(V(GRAPH_OBJECT)$name %in% NAMES_TO_REMOVE)
    GRAPH_OBJECT <-  delete.vertices(GRAPH_OBJECT, VERTICES_TO_REMOVE)
    return(GRAPH_OBJECT)
}
```




# Run Functions
## Set variables
```{r}
Edge_Matrix_ID <- SEMANTIC_EDGES_MATRIX # The adjacency edge matrix that is inputed in functions
Child_Dataframe <-  Child_Dataframe # The dataset that contains all information regarding the children
ID_collumn_name <- "child_id"
Age_collumn_name <- "age"
Unique_Children <- FUNC_Get_List_Of_Unique_Child_ID(Child_Dataframe, ID_collumn_name)
Child_ID <- Unique_Children[6]
Is_word_known_collumn_name = "value"
Word_string_collumn_name = "item_definition"

```


## Execution Block

```{r}
# Run for one child, find subset


child_1414_1<- FUNC_Subset_child_at_first_unique_age(
    dataframe = Child_Dataframe,
    ID_collumn_name = ID_collumn_name,
    ID_String =  Child_ID,
    Age_collumn_name =  Age_collumn_name)

# Make adj matrix
Personalized_Adj_Matrix <- FUNC_Get_known_words_matrix(
    Subset_dataframe = child_1414_1,
    Is_word_know_collumn_name =  Is_word_known_collumn_name,
    Word_string_collumn_name = Word_string_collumn_name)

# Get semantic adj matrix
Personalized_Adj_Linguistic_Matrix <- 
    FUNC_Personalised_ling_adj_matrix(
    Personalized_Matrix = Personalized_Adj_Matrix,
    Linguistic_Matrix = SEMANTIC_EDGES_MATRIX)


```


# Create a GRAPH
```{r}
GRAPH<- FUNC_Create_a_Graph_And_Remove_unknown_words(
    Subset_dataframe = child_1414_1,
    Personalized_Adj_Linguistic_Matrix = Personalized_Adj_Linguistic_Matrix, 
    Is_word_know_collumn_name = Is_word_known_collumn_name,
    Word_string_collumn_name =  Word_string_collumn_name)




```

