---
title: "Creating_Networks_From_Functions"
author: "Laurits og Tilde (klag til laurits hvis noget er galt)"
date: "2023-10-10"
output: html_documentn
---
# SETUP
## Load packages
```{r}
### install.packages("pacman")
pacman::p_load(tidyverse, igraph, purrr)
```

## Load files into into the environment
All files need to be either the child data or a cleaned adjacency matrix:
```{r}

# Load the child data
Child_Dataframe <- read_csv(file = "../../Bachelor/Data/Cleaned_USA.csv") %>% #Subset of data for quick functions
    arrange(item_definition) %>% # sorter dataen
    arrange(child_id) %>%
    arrange(age) %>%
    distinct(child_id, age,item_definition, .keep_all = TRUE) #Make sure all children are 618 length matrix, by removing duplicates

# Load semantics df
SEMANTIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/SEMANTIC_EDGES_MATRIX.txt", sep = ","))

# Load phonetic distance df
PHONETIC_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/PHONETIC_EDGES_MATRIX.txt", sep = ","))

# Load distance df
WORD_LENGTH_EDGES_MATRIX <- as.matrix(read.delim(file = "../Data/Cleaned/WORD_LENGTH_EDGES_MATRIX.txt", sep = ","))
```

```{r}
# Save MATRICES for looping
PSYCHOLING_EDGE_MATRICES <- list(SEMANTIC_EDGES_MATRIX, PHONETIC_EDGES_MATRIX, WORD_LENGTH_EDGES_MATRIX)
PSYCHOLING_STRING <- list("SEMANTIC", "PHONETIC", "WORD_LENGTH")
```


# Define Functions
## Create a function that defines a adjacency matrix of words known for a unique child at unique timepoint
```{r}
Remove_Self_Edges <- function(Subset_dataframe, Is_word_know_collumn_name, Word_string_collumn_name){
# Remove edges between words that are connected to themselves 
    ID_MATRIX <- diag(length(KNOWN_WORDS_IDENTIFICATION_MATRIX[1,])) # Create a identity matrix of length(adjaceny_matrix)
    REMOVE_SELF_EDGES <- KNOWN_WORDS_IDENTIFICATION_MATRIX*ID_MATRIX # Create a matrix that has a 1 if the word triggers an edge with itself.
    KNOWN_WORDS_IDENTIFICATION_MATRIX <- KNOWN_WORDS_IDENTIFICATION_MATRIX - REMOVE_SELF_EDGES # Remove self edges from known words matrix
    return(KNOWN_WORDS_IDENTIFICATION_MATRIX)   
}
```




## Use Known_words_matrix to create a personalized ADJ_MATRIX for a linguistic adj matrix 
```{r}
FUNC_Personalised_ling_adj_matrix <- function(Personalized_Matrix, Linguistic_Matrix){
    #' This function takes two equally sized matrix' and multiplies them, this results in only edges between words known to the child being saved.
    Personalized_Linguistic_Matrix <- Personalized_Matrix * Linguistic_Matrix
    return(Personalized_Linguistic_Matrix)}

FUNC_Get_adj_matrix_merged <- function(
        List_of_subsets,
        Is_word_know_collumn_name,
        Word_string_collumn_name,
        Linguistic_Matrix)
    {
    # NEEDS: List_of_subsets, Is_word_know_collumn_name, Word_string_collumn_name,
    # Make adj matrix' (0.80 seconds at subset -> 8.02 seconds at full dataset)
    List_of_personalized_adj_matrix <- purrr::map(
        .x = List_of_subsets,
        .f = FUNC_Get_known_words_matrix,
        Subset_dataframe = , #left empty to show .x map value
        Is_word_know_collumn_name =  Is_word_known_collumn_name,
        Word_string_collumn_name = Word_string_collumn_name)
    
    # NEEDS EDGE MATRIX AND PERSONAL MATRIX
    # Convert the personalized matrix to a linguistically corrected matrix (0.223 seconds)
    List_of_personalized_adj_matrix <- purrr::map(
        .x = List_of_personalized_adj_matrix, 
        .f = FUNC_Personalised_ling_adj_matrix,
        Personalized_Matrix = ,#left empty to show .x map value
        Linguistic_Matrix = Linguistic_Matrix)
    
    return(List_of_personalized_adj_matrix)
}
```

# Get known words
```{r}
FUNC_Create_a_Graph_And_Remove_unknown_words <- function(Subset_dataframe,
                                                         Personalized_Adj_Linguistic_Matrix,
                                                         Is_word_know_collumn_name, 
                                                         Word_string_collumn_name){
    #' Requires IGRAPH package
    GRAPH_OBJECT <- graph_from_adjacency_matrix(Personalized_Adj_Linguistic_Matrix, mode = "undirected")
    NAMES_TO_REMOVE <- FUNC_Subset(dataframe = Subset_dataframe,
                column_name = Is_word_know_collumn_name,
                true_value = 0)
    NAMES_TO_REMOVE <- NAMES_TO_REMOVE[[Word_string_collumn_name]]
    VERTICES_TO_REMOVE <- which(V(GRAPH_OBJECT)$name %in% NAMES_TO_REMOVE)
    GRAPH_OBJECT <-  delete.vertices(GRAPH_OBJECT, VERTICES_TO_REMOVE)
    return(GRAPH_OBJECT)
}
```

## Create a function that duplicate your graph in a named list for each 
```{r}
FUNC_Tranform_graph_to_list_of_graphs <-  function(GRAPH_OBJECT, KNOWN_WORDS_STRING){
    NESTED_GRAPH <- list(GRAPH_OBJECT) # Wrap list to allow for rep
    LIST_OF_GRAPHS <- rep(NESTED_GRAPH,length(KNOWN_WORDS_STRING)) # Repeat list 618 times
    names(LIST_OF_GRAPHS) <-  KNOWN_WORDS_STRING # Name the graphs
    return(LIST_OF_GRAPHS)
}
```

## Create a function that adds a new word and its edges to the graph
```{r}

FUNC_Add_new_word_to_graph <- function(GRAPH_OBJECT, NEW_WORD_STRING, ADJ_MATRIX){
    if (NEW_WORD_STRING %in% V(GRAPH_OBJECT)$name){
        return(GRAPH_OBJECT)
    }
    
    VECTOR_OF_NAMES <- colnames(ADJ_MATRIX) # GET A VECTOR OF STRING TO BE ABLE TO which(vector == "value"), as matrix[,"x"] breaks with certain strings
    ### Only pick the semantic edges for NEW_WORD_STRING
    EDGES <- ADJ_MATRIX[,which(VECTOR_OF_NAMES == NEW_WORD_STRING)]
    
    ### Save verticies (words) from graph:
    VERTICES_IN_GRAPH <- V(GRAPH_OBJECT)$name
    
    
    NAMED_EDGES_OF_VERTICIES <- EDGES[names(EDGES) %in% VERTICES_IN_GRAPH]
    EDGES_OF_VERTICIES <- names(NAMED_EDGES_OF_VERTICIES[which(NAMED_EDGES_OF_VERTICIES==1)])
    
    #Make df into a string again
    EDGE_LIST <- c(
        rbind( # Bind NEW_WORD_STRING before each edge
            NEW_WORD_STRING,EDGES_OF_VERTICIES))
    
    
    if (length(EDGE_LIST) > 1){
        GRAPH_OBJECT <- GRAPH_OBJECT + 
            NEW_WORD_STRING + #insert vertice without edges
            edges(EDGE_LIST) #add edges from vertice to other vertices
    } else {
        GRAPH_OBJECT <- GRAPH_OBJECT + NEW_WORD_STRING
    }
    
    return(GRAPH_OBJECT)
}

## NESTED VERSION
# Return_list_of_updated <- imap(List_of_List_of_Graphs[[1]], FUNC_nested_add_word_to_graph_for_imap, MATRIX = SEMANTIC_EDGES_MATRIX)
FUNC_nested_add_word_to_graph_for_imap <- function(igraph_object, index, MATRIX) {
    #' Add the new word to the igraph
    igraph_object <- FUNC_Add_new_word_to_graph(
        GRAPH_OBJECT = igraph_object,
        NEW_WORD_STRING = index,
        ADJ_MATRIX = MATRIX)
    return(igraph_object)  # You can return the modified graph or any other result
}




```

# Run Functions
## Set variables
```{r}
Child_Dataframe <-  Child_Dataframe # The dataset that contains all information regarding the children, CURRENTLY subset.
ID_collumn_name <- "child_id"
Age_collumn_name <- "age"
Word_string_collumn_name = "item_definition"
Word_numeric_column_name = "item_id"
Is_word_known_collumn_name = "value"
```

### Set Lists of subsets:
```{r}
Unique_Children <- FUNC_Get_List_Of_Unique_Child_ID(Child_Dataframe, ID_collumn_name)
# List of subsets
List_of_subsets <- as.list(setNames(Unique_Children, Unique_Children))

# Time specific versions
List_of_subsets_t1 <- purrr::map(
   .x =  List_of_subsets, 
   .f = FUNC_Subset_child_at_first_unique_age,
   dataframe = Child_Dataframe,
   ID_collumn_name = ID_collumn_name,
   Age_collumn_name = Age_collumn_name,
   ID_String = ) #Nothing defined here to show that the map .x map value is used
List_of_subsets_t2 <- purrr::map(
   .x =  List_of_subsets, 
   .f = FUNC_Subset_child_at_second_unique_age,
   dataframe = Child_Dataframe,
   ID_collumn_name = ID_collumn_name,
   Age_collumn_name = Age_collumn_name,
   ID_String = ) #Nothing defined here to show that the map .x map value is used

List_of_list_of_subsets <- list(List_of_subsets_t1, List_of_subsets_t2)
```


```{r}
KNOWN_WORDS_NUMERIC <- unique(Child_Dataframe[[Word_numeric_column_name]]) 
KNOWN_WORDS_STRING <-  unique(Child_Dataframe[[Word_string_collumn_name]]) 
KNOWN_WORDS_STRING[75] <- "breaks" # Changed from break to avoid making funcitons stop
```

```{r}
Running_all_functions <- function(
        List_of_subsets,
        Is_word_known_collumn_name,
        Word_string_collumn_name,
        KNOWN_WORDS_STRING,
        Linguistic_Matrix,
        Timepoint,
        PSY_NAME){
    #' First function
        List_of_personalized_adj_matrix <- FUNC_Get_adj_matrix_merged(
            List_of_subsets = List_of_subsets,
            Is_word_know_collumn_name =  Is_word_known_collumn_name,
            Word_string_collumn_name = Word_string_collumn_name,
            Linguistic_Matrix = Linguistic_Matrix)
    #' Second function
        List_of_graphs <- purrr::map2(
            .x = List_of_subsets,
            .y = List_of_personalized_adj_matrix,
            .f = FUNC_Create_a_Graph_And_Remove_unknown_words,
            Is_word_know_collumn_name = Is_word_known_collumn_name,
            Word_string_collumn_name =  Word_string_collumn_name,
            Subset_dataframe = )#This is where .x parameter goes
    #' Third function
        List_of_List_of_graphs <- purrr::map(
            .x = List_of_graphs,
            .f = FUNC_Tranform_graph_to_list_of_graphs,
            GRAPH_OBJECT = ,#This is where .x parameter goes
            KNOWN_WORDS_STRING = KNOWN_WORDS_STRING)
        
    #' Fourth function
        List_of_List_of_graphs <- purrr::map(.x = List_of_List_of_graphs,.f =  function(inner_list) {
            imap(
                .x = inner_list,
                .f =  FUNC_nested_add_word_to_graph_for_imap, 
                MATRIX = Linguistic_Matrix)})
        
    #' Fifth function
        List_of_centrality <-  purrr::map(List_of_List_of_graphs, function(inner_list) {
            imap(inner_list, function(graph_object, index){
                eigen_centrality(graph_object, directed = FALSE)$vector[index] })}) # CHANGE HERE FOR DIFFERENT CENTRALITY MEASSUREMENT
        
        DF_Centrality <- rrapply::rrapply(List_of_centrality, how = "melt") %>%
            rename(Child_ID = L1, item_definition = L2) %>% 
            mutate(Timepoint = Timepoint,
                   value = format(value, scientific = FALSE,),
                   Linguistic_var = PSY_NAME)
        return(DF_Centrality)
}
```




## Execution Block
```{r}
for (i in 1:length(PSYCHOLING_EDGE_MATRICES)){
    PSY_NAME <- PSYCHOLING_STRING[[i]]
    PSY_MATRIX <- PSYCHOLING_EDGE_MATRICES[[i]]  # The adjacency edge matrix that is inputed in functions
    for (i_subset in 1:2){
        List_of_subsets <- (List_of_list_of_subsets[[i_subset]])
        DF_Centrality <- Running_all_functions(
            List_of_subsets = List_of_subsets,
            Is_word_known_collumn_name = Is_word_known_collumn_name,
            Word_string_collumn_name = Word_string_collumn_name,
            KNOWN_WORDS_STRING = KNOWN_WORDS_STRING,
            Linguistic_Matrix = PSY_MATRIX,
            Timepoint = i_subset,
            PSY_NAME = PSY_NAME)
        
        save_as_file_path <- paste0("../Data/Lexcial_information/",PSY_NAME,"_time_", i_subset,".csv")
        write.csv(x = DF_Centrality, file = save_as_file_path)
        }} 
```











