This is where we manually do the magic??! ;)

```{r}
# Load packages, and download if not locally stored
pacman::p_load(tidyverse, igraph)
```

# Single out a child, and a timepoint
```{r}
# Read dataset
Words_known_for_child <- read.csv("../Data/75kidsubset.csv") %>% 
    mutate(word_length = nchar(item_definition))# Create vector of word_length
```

```{r}
# Create vector of all child ID's
Unique_Child_IDs <- unique(Words_known_for_child$child_id)

# Filter vector to only be for child N at first timepoint
N <- 1 # The child we want to investigate
filtered_Words_for_child <- Words_known_for_child %>% 
    filter(child_id == Unique_Child_IDs[N]) %>% #Only pick the N'th child
    filter(age == min(age))



## Test to check filtering worked correct:)
# filtered_Words_for_child %>% 
#     select(age, child_id) %>% 
#     unique
```

## Create an adj_matrix  
```{r}
# Create a vector of words used
words <- filtered_Words_for_child$uni_lemma

# Save vector of word_length
word_length_vec <- filtered_Words_for_child$word_length

#Create adjacency matrix
adjacency_matrix <- matrix(abs(outer(word_length_vec,word_length_vec, FUN = "-")), # Create values for matrix
                           nrow = length(words), ncol = length(words), # Define size of matrix
                           dimnames = list(words, words)) #Give names to dimensions

#Use ifelse as a vectorized function on the matrix
adjacency_matrix <- ifelse(adjacency_matrix<=1,yes = 1, 0)
id_matrix <- diag(length(adjacency_matrix[1,])) # Create a identity matrix of length(adjaceny_matrix)
adjacency_matrix <- adjacency_matrix-id_matrix

```


# Create an igraph object
```{r}
graph_object <- igraph::graph_from_adjacency_matrix(adjacency_matrix)
```


### Find data for timepoint two
```{r}
# Create vector of all child ID's
Unique_Child_IDs <- unique(Words_known_for_child$child_id)

# Filter vector to only be child N at first timepoint

N <- 1 # The child we want to investigate
Time_N <- 1 # The timepoint for this child
filtered_Words_for_child1_t1 <- Words_known_for_child %>% 
    filter(child_id == Unique_Child_IDs[N]) %>% #Only pick the N'th child
    arrange(age) %>%
    filter(age == unique(age)[Time_N])

#Repeat filter chunk to save timepoint 2
Time_N <- 2
filtered_Words_for_child1_t2 <- Words_known_for_child %>% 
    filter(child_id == Unique_Child_IDs[N]) %>% 
    arrange(age) %>%
    filter(age == unique(age)[Time_N])

count(filtered_Words_for_child, age)
filtered_Words_for_child %>% 
    group_by(age) %>% 
    count(value)

```

# TRYING TO SAVE ALL GRAPHS IN A VECTOR AND RUN A FUNCTION ON THAT VECTOR
## STEP 1: Create a vector of words that need to be added to t1 graph (all words at t2-all words at t1), and then a vector of words that need to be tested (all words at t2)

```{r}
All_words_at_t1 <- filtered_Words_for_child1_t1 %>%
    mutate(value_t1 = value) %>% 
    select(item_definition,value_t1)
All_words_at_t1 <- All_words_at_t1$item_definition


All_words_at_t2 <- filtered_Words_for_child1_t2 %>%
mutate(value_t2 = value) %>% 
    select(item_definition,value_t2)
All_words_at_t2 <- All_words_at_t2$item_definition


words_merge<- merge(All_words_at_t1,All_words_at_t2)


t2_words_notin_t1 <- setdiff(All_words_at_t2, All_words_at_t1)


which(!(All_words_at_t1 %in% All_words_at_t2))
```










































# Create my lag function
```{r}
my_lag_function <- function(string,shift){
    # Takes a vector of strings and shifts the n final strings to beginning. The n amount is decided by shift.
    length_of_string <- length(string)
    
    output <- c(test[(length_of_string-shift+1):length_of_string],test[1:(length_of_string-shift)])
    return(output)
}
```







